From Light to GDP: A Study of Night-Time Light as an Indicator of Economic Development

### 2024-12-05 paper/paper.qmd
cited R and Python.

The data preparation began with extracting night-time light (NTL) intensity values from GeoTIFF files using Python's 'Rasterio' [@raster] package. This process involved reading annual TIFF files to obtain Digital Number (DN) values, representing light intensity, along with their corresponding latitude and longitude coordinates. This resulted in a spatial dataset detailing global NTL distribution for each year.

To associate each observation with a specific country, the extracted data were merged with a global shapefile of country boundaries through spatial join using 'geopandas' [@geopandas]. Each latitude-longitude pair was assigned to the country in which it was located, and observations without an assigned country—primarily from international waters—were removed. Subsequently, to create an aggregate annual measure of NTL intensity for each country, all observations within a country were summed to calculate the total light emitted annually.

@@

In the first model, we examine the relationship between Night-Time Light (NTL) intensity and GDP, controlling for country and year-specific fixed effects. The coefficient for log(GDP) is positive and significant (0.974), indicating that a 1% increase in GDP corresponds to an approximately 0.97% increase in NTL intensity on average. The R² value of 0.958 suggests that the model explains 95.8% of the variation in NTL, highlighting a strong relationship. The inclusion of fixed effects ensures that unobserved heterogeneity, such as geographic or temporal factors, is accounted for.

>>>>

The data preparation began with extracting night-time light (NTL) intensity values from GeoTIFF files using Python' 'Rasterio' [@raster] package. This process involved reading annual TIFF files to obtain Digital Number (DN) values, representing light intensity, along with their corresponding latitude and longitude coordinates. This resulted in a spatial dataset detailing global NTL distribution for each year.

To associate each observation with a specific country, the extracted data were merged with a global shapefile of country boundaries through spatial join using 'geopandas' [@geopandas] in python [@python312]. Each latitude-longitude pair was assigned to the country in which it was located, and observations without an assigned country—primarily from international waters—were removed. Subsequently, to create an aggregate annual measure of NTL intensity for each country, all observations within a country were summed to calculate the total light emitted annually.

@@

All models were fit using the built-in lm function in R [@citeR]. In the first model, we examine the relationship between Night-Time Light (NTL) intensity and GDP, controlling for country and year-specific fixed effects. The coefficient for log(GDP) is positive and significant (0.974), indicating that a 1% increase in GDP corresponds to an approximately 0.97% increase in NTL intensity on average. The R² value of 0.958 suggests that the model explains 95.8% of the variation in NTL, highlighting a strong relationship. The inclusion of fixed effects ensures that unobserved heterogeneity, such as geographic or temporal factors, is accounted for.
